### 2018-07-11 Stickleback_Paper.tex
latest

%(2) Do the math, discuss number ( and possibly type ) of mutations underlying the trait value.
\subsection*{do the math}
\jgg{peter? :)}

@@

@@

We also have also explored the genomic architecture as a consequence of the nature of selection in our scenario. 
The alleles underlying individual trait value were of large effect and a low number. 
With a total of $10^{5}$ loci, to be realistic, each loci should represent 1000 $Kb$ in real data.

We have also shown introgression is beneficial for inferring causative loci from divergence ($F_{st}$) along the genome. 
%wouldn't it be cool if we could use this fact and simulate introgression, starting with real data that is noisy to extrapolate the areas we care about?
%this could be nonsense

@@

We have found that too little migration leads to selection upon new mutations in all subpopulations and lakes alike. 
In contrast, at high migration rates we have seen that migration load limits 
the ability for species to locally adapt to the selective pressure of their environment.
This leads us to consider a window (Goldilocks Zone) of introgression which allows for the transportation
of FAA's without migration load. In a species that commonly is subjected to two general types of selective pressure 
such as marine and freshwater stickleback this is suggestive of the benefit of hybridization in all subpopulations before
reaching a point of pre or post zygotic

%(3) discuss what signals researchers could possibly look out for or connect to real data
\subsection*{signals and real data}

>>>>

%(2) Do the math, discuss number ( and possibly type ) of mutations underlying the trait value.

@@

\subsection*{do the math}
\jgg{peter? :)}

(1) - What is the mean fitness of a population

(2) - assuming everybody is at the mean fitness, what is the expected num of offspring after t gens in marine

(3) - expected num of establishing alleles in new lake. = (num outmigrants) $\times$ (num per outmigrant) $\times$ (prob migrant) $\times$ $2\hat{x}s $ mean fit in new lake

@@

We also have also explored the genomic architecture as a consequence of the nature of selection in our scenario. 
The alleles underlying individual trait value were of large effect and a low number. 
With a total of $10^{5}$ loci, to be realistic, each loci should represent 1000 $Kb$ in real data.
\jgg{This should be expanded upon, not sure what this means in terms of the genomic architecture}

We have also shown introgression is beneficial for inferring causative loci from divergence ($F_{st}$) along the genome. 
This is generally because noise of selectively neutral alleles divergence can appear causative when genetic drift causes more 
differences between populations that have little gene flow between them.
It's important to know that in all scenarios, hitchhiking of selectively neutral alleles could also be 
mistaken for being causative as they often display the same amount of divergence.
%wouldn't it be cool if we could use this fact and simulate introgression, starting with real data that is noisy to extrapolate the areas we care about?
%this could be nonsense

@@

We have found that too little migration leads to selection upon new mutations in all subpopulations and lakes alike. 
In contrast, at high migration rates we have seen that migration load limits 
the ability for species to locally adapt to the selective pressure of their environment.
This leads us to consider a window of introgression which allows for the transportation
of FAA's without migration load.

\subsection*{connect results back to real data?}

%In a species that commonly is subjected to two general types of selective pressure 
%such as marine and freshwater stickleback this is suggestive of the benefit of hybridization in all subpopulations before
%reaching a point of pre or post zygotic

%(3) discuss what signals researchers could possibly look out for or connect to real data
